Bayesian Mixed Effects Models - Training Data

### 2024-03-11 Analysis/brms_learning.qmd
tweaks

nlform <- bf(
  dist ~ a + (b - a) * exp(-c * gt.train),
  a ~ 0 + condit + (1|bandInt) + (1|id), 
  b ~ 0 + condit + (1|bandInt)  + (1|id), 
  c ~ 0 + condit + (1|id), 
  nl = TRUE 
)

>>>>

nlform <- bf(
  dist ~ a + (b - a) * exp(-c * gt.train),
  a ~ 0 + condit + (1|bandInt) + (1|id), 
  b ~ 0 + condit + (1|bandInt)  + (1|id), 
  c ~ 0 + condit + (1|bandInt) + (1|id), 
  nl = TRUE 
)

### 2024-03-11 Analysis/combo_train.qmd
tweaks

```{r}

# fit exponential decay model as a function of trial number

@@

avgTrain <- dst %>% group_by(id,condit,trial,band,input) %>% summarise(dist=mean(dist)) %>% ungroup() %>% group_by(condit,trial,band) %>% summarise(dist=mean(dist)) %>% ungroup()

ggplot(avgTrain,aes(x=trial,y=dist)) + geom_line(aes(group=band,color=band)) +facet_grid(~condit)

avgTrain %>% filter(condit=="Constant") %>% nls(dist ~ yf + (y0-yf) * exp(-r*trial), start = list(yf = 120, y0 = 364, r = .1), data = .) %>% summary()

avgTrain %>% filter(condit=="Constant") %>% nls(dist ~ SSasymp(trial, yf, y0, log_alpha),data=.)

fit_condit <- avgTrain %>% group_by(condit) %>% do(fit_exp(trial=.$trial,dist=.$dist,input=.$input))

>>>>

```{r}
#| eval: false
# fit exponential decay model as a function of trial number

@@

avgTrain <- e1 |> filter(expMode2=="Train") %>% group_by(id,condit,gt.train,vb,bandInt) %>% 
  summarise(dist=mean(dist)) %>% ungroup() %>% 
  group_by(condit,gt.train,vb,bandInt) %>% 
  summarise(dist=mean(dist)) %>% ungroup()

ggplot(avgTrain,aes(x=gt.train,y=dist)) + geom_line(aes(group=vb,color=vb)) +facet_grid(~condit)

avgTrain %>% filter(condit=="Constant") %>% nls(dist ~ yf + (y0-yf) * exp(-r*gt.train), start = list(yf = 120, y0 = 364, r = .1), data = .) %>% summary()

avgTrain %>% filter(condit=="Constant") %>% nls(dist ~ SSasymp(gt.train, yf, y0, log_alpha),data=.)

fit_condit <- avgTrain %>% group_by(condit) %>% do(fit_exp(trial=.$gt.train,dist=.$dist,input=.$bandInt))

#avgTrain %>% group_by(condit) |> mutate(fit=map(~fit_exp(trial=gt.train,dist=dist,input=bandInt)))
